---
title: "README"
author: "Shynggys Magzanov"
date: "09 09 2020"
output:
  pdf_document: default
  html_document: default
---
```{r,eval=FALSE}
devtools::install_github("hadley/sloop")
devtools::install_github("hadley/emo")
```
The first error that occured is:
##There is no package called ‘devtools’

So it was installed.

install.packages("devtools")


install.packages("bookdown")

```{r render, eval = FALSE}
bookdown::render_book("index.Rmd", output_format = "bookdown::pdf_book")
````
The second error that occured is:
##Quitting from lines 123-126 (Introduction.Rmd) 
##Error in Rscript_render(f, render_args, render_meta, add1, add2) : 
##Failed to compile Introduction.Rmd

Fixed by installing the package 'dplyr'

install.packages("dplyr")

The third error that occured is:
##Quitting from lines 80-81 (Names-values.Rmd) 
##Error in Rscript_render(f, render_args, render_meta, add1, add2) : 
##Failed to compile Names-values.Rmd

Fixed by installing the package 'lobstr'

install.packages("lobstr")

The fourth error that occured is:
##Quitting from lines 432-434 (Names-values.Rmd)
##Error in Rscript_render(f, render_args, render_meta, add1, add2) : 
##Failed to compile Names-values.Rmd

Fixed by installing 'ggplot2'

install.packages("ggplot2")

The fifth error that occured is:
##Quitting from lines 535-550 (R6.Rmd)
##Error in Rscript_render(f, render_args, render_meta, add1, add2) : 
##Failed to compile R6.Rmd

Fixed by installing 'DBI'

install.packages("DBI")

The sixth error that occured is:
##Quitting from lines 535-550 (R6.Rmd)
##Error in Rscript_render(f, render_args, render_meta, add1, add2) : 
##Failed to compile R6.Rmd

Fixed by installing 'RSQLite'

install.packages("RSQLite")

The seventh error that occured is:
##Quitting from lines 172-176 (OO-tradeoffs.Rmd)
##Error in Rscript_render(f, render_args, render_meta, add1, add2) : 
##Failed to compile OO-tradeoffs.Rmd

Fixed by installing 'zeallot'

install.packages("zeallot")

The 8th error that occured is:
##Quitting from lines 209-221 (Big-picture.Rmd)
##Error in Rscript_render(f, render_args, render_meta, add1, add2) : 
##Failed to compile Big-picture.Rmd

Fixed by installing the package 'dbplyr'

install.packages("dbplyr")

The 9th error that occured is:
##Quitting from lines 38-40 (Perf-measure.Rmd) 
##Error in Rscript_render(f, render_args, render_meta, add1, add2) : 
##Failed to compile Perf-measure.Rmd

Fixed by installing the package 'profvis'

install.packages("profvis")

The 10th error that occured is:
##Quitting from lines 38-40 (Perf-measure.Rmd) 
##Error in Rscript_render(f, render_args, render_meta, add1, add2) : 
##Failed to compile Perf-measure.Rmd

Fixed by installing the package 'bench'

install.packages("bench")

The 11th error that occured is:
##Failed with error:  'there is no package called 'tidyr''
##Error in Rscript_render(f, render_args, render_meta, add1, add2) : 
##Failed to compile Perf-measure.Rmd

Fixed by installing the package 'tidyr'

install.packages("tidyr")

The 12th error that occured is:
##Quitting from lines 233-234 (Perf-measure.Rmd) 
##Error in Rscript_render(f, render_args, render_meta, add1, add2) : 
##Failed to compile Perf-measure.Rmd

Fixed by installing the package 'ggbeeswarm'

install.packages("ggbeeswarm")

The 13th error that occured is:
##Quitting from lines 77-84 (Rcpp.Rmd) 
##Error in sourceCpp(code = code, env = env, rebuild = rebuild, cacheDir = cacheDir,  : 
##Error 1 occurred building shared library.
##Calls: local ... withVisible -> eval -> eval -> cppFunction -> sourceCpp

Fixed by installing RTools40 and putting the location of the Rtools make utilities (bash, make, etc) on the PATH

The 14th error that occured is:
##xelatex"' not foundError: LaTeX failed to compile _main.tex. See https://yihui.org/tinytex/r/#debugging for debugging tips.

Seems like my TinyTex was actually broken, and doing the following helped to fix the problem:

tinytex:::install_prebuilt()

The 15th error that occured is:
##Package fontspec Error: The font "Inconsolata" cannot be found.

Fixed by downloading and installing the font from the web. Also reinstalled "tinytex" package. Took 100500 tries to handle this error.

Finally I was able to render the book in a pdf. 



